---
title: "Lostine River Weir Steelhead Update"
author: "Brian Simmons"
date: "`r Sys.Date()`"
output: 
  html_document:
    css: ../www/style.css
    theme: readable
    toc: false #notice changes in indentation. indentation MUST be correct for YAML header
    toc_depth: 2
    toc_float:
      collapsed: true
      smooth_scroll: false
    includes:
      in_header: npt_joseph.html
      # before_body: npt_joseph.html # includes the header to the right of the toc same width as report body.
---

```{r setup, include=FALSE}
#Set up global code chunk options for document
library(tidyverse)
library(flextable)
# library(cdmsR)
# library(cuyem)

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)


options(knitr.kable.NA = '-')
```

```{r packages, include = FALSE, eval = FALSE}
# devtools::install_github("DesiQuintans/librarian") # if you need librarian package

librarian::shelf(knitr,
                 flextable,
                 ryankinzer/cdmsR,
                 ryankinzer/cuyem,
                 tidyverse)

```




```{r data-import, include = FALSE}

# Uncomment and load to get new data
# cdmsLogin('brians','bs2018')

# tmp1 <- get_WeirData(Facility = "NPT GRSME Program",
#                               Species = "Steelhead")
# tmp2 <- get_WeirData(Facility = "NPT GRSME Program",
#                         Species = "Rainbow Trout")
# tmp3 <- get_WeirData(Facility =  "NPT GRSME Program",
#                         Species = "Bull Trout")
# 
# 
# lrw_omykiss <- bind_rows(tmp1, tmp2, tmp3) %>%
#   clean_weirData() %>%
#   mutate(trapped_date = ymd(trapped_date),
#          MonthDay = format(as.Date(trapped_date), '%m/%d'))
# 
# rm(tmp1, tmp2, tmp3)
# 
# save(lrw_omykiss, file = '../data/lrw_omykiss.rda')
# rm(lrw_omykiss)

load('../data/lrw_omykiss.rda')
source('../R/07_sumSTHdisp.R')
source('../R/07_sumRBTdisp.R')
source('../R/07_sumSTHweekly.R')

trap.year <- 2023
yr_range <- (trap.year-9):trap.year


```




```{r figure-theme, message = FALSE, include = FALSE}

# Figure Settings
theme_set(theme_bw() +
          theme(panel.grid  = element_blank(),
                panel.background = element_blank(),
                legend.position = 'bottom',
                text = element_text(family = 'sans'),
                plot.title = element_text(hjust = 0.5),
                plot.subtitle = element_text(hjust = 0.5)
          ))

```

```{r Data Processing: Dispositions, include=FALSE}

# I dont know what all this gets me, or if the data are correct...

# Hatchery Dispositions
hsth_df <- sumSTHdisp(data = lrw_omykiss, origin_ ='Hatchery', trap.year = trap.year)

# Natural Dispositions
nsth_df <- sumSTHdisp(data = lrw_omykiss, origin_ ='Natural', trap.year = trap.year)

# Natural Rainbow Dispositions
nrbt_df <- sumRBTdisp(data = lrw_omykiss, origin_ = 'Natural', trap.year = trap.year)

# Hatchery Rainbow DDispositions
hrbt_df <- sumRBTdisp(data = lrw_omykiss, origin_ = 'Hatchery', trap.year = trap.year)


# Composition Percentages
hat_up <- as.numeric(str_extract(hsth_df[[1,4]], '^[:digit:]*')) # upstream
nat_up <- as.numeric(str_extract(nsth_df[[1,4]], '^[:digit:]*')) # upstream
  H_upstream_calc <- round((hat_up/(hat_up+nat_up))*100, 0)

hat_BS <- as.numeric(str_extract(hsth_df[[2,4]], '^[:digit:]*')) # broodstock
nat_BS <- as.numeric(str_extract(nsth_df[[2,4]], '^[:digit:]*')) # broodstock
  N_brood_calc <- round((nat_BS/(hat_BS+nat_BS))*100, 0)

```

```{r}

# Flow Data ----
start_date <- paste0(trap.year, '-03-01')
end_date <- paste0(trap.year, '-08-01')

req_url <- paste("https://apps.wrd.state.or.us/apps/sw/hydro_near_real_time/hydro_download.aspx?station_nbr=13330000&start_date=",
                 start_date, # start date
                 "%2012:00:00%20AM&end_date=",
                 end_date, #Sys.Date(), # end date
                 "%2012:00:00%20AM&dataset=MDF&format=csv",  # output: CSV
                 sep='')

flow_df <- read.delim(req_url, sep = '\t') %>%
  mutate(record_date = mdy(record_date),
         legend = paste(Sys.Date()-1, 'Discharge'),
         MonthDay = format(as.Date(record_date), '%m/%d'),
         facet = paste(trap.year)) %>%
  select(MonthDay, MeanDailyFlow = mean_daily_flow_cfs, facet) 

start_date_H <- paste0(trap.year-5, '-03-01')
end_date_H <- paste0(trap.year-1, '-08-01')

req_url2 <- paste("https://apps.wrd.state.or.us/apps/sw/hydro_near_real_time/hydro_download.aspx?station_nbr=13330000&start_date=",
                  start_date_H, # start date
                  "%2012:00:00%20AM&end_date=",
                  end_date_H, # end date
                  "%2012:00:00%20AM&dataset=MDF&format=csv",  # output: CSV
                  sep='')

flow_df_H <- read.delim(req_url2, sep = '\t') %>%
  mutate(record_date = mdy(record_date),
         legend = paste(Sys.Date()-1, 'Discharge'),
         MonthDay = format(as.Date(record_date), '%m/%d')) %>%
  group_by(MonthDay) %>%
  summarize(MeanDailyFlow = mean(mean_daily_flow_cfs)) %>%
  mutate(facet = paste(trap.year-5, '-', trap.year-1, " Average", sep=''))

flow_all <- bind_rows(flow_df, flow_df_H) %>%
  mutate(trapped_date = paste(trap.year, '/', as.character(MonthDay), sep = ''),
         trapped_date = ymd(trapped_date)) %>% # trapped date cheat.
  filter(between(trapped_date, ymd(paste0(trap.year, '-03-01')), ymd(paste0(trap.year, '-08-01'))))



# Current year's catch ----
LRW_catch <- lrw_omykiss %>%
  filter(species == 'Steelhead',
         recap == FALSE,
         trap_year == trap.year) %>%
  group_by(trapped_date, MonthDay, origin) %>%
  summarize(Catch = sum(count, na.rm = TRUE)) %>%
  mutate(facet = paste(trap.year))

# Historic Catch ----
LRW_historic <- lrw_omykiss %>%
  filter(facility == 'NPT GRSME Program', 
         species == 'Steelhead',
         recap == FALSE,
         !trap_year %in% c(1997:(trap.year-6), trap.year)) %>% # exclude everything 1997 to trap year-6 & the trap year
  group_by(MonthDay, origin) %>%  # get the total catch for Month/Day
  summarize(AllCatch = sum(count, na.rm = TRUE)) %>%
  mutate(Catch = AllCatch/5) %>% # calculate Mean Daily Catch: AllCatch from years, divided by number of years (5)
  mutate(trapped_date = ymd(paste(trap.year, '-', MonthDay)),
         facet = paste(trap.year-5, '-', trap.year-1, " Average", sep=''))

LRW_all <- bind_rows(LRW_catch, LRW_historic)

# MEGA DF!
LRW_megadf <- full_join(LRW_all, flow_all, by = c('trapped_date', 'facet', 'MonthDay'))

LRW_megadf$facet <- factor(LRW_megadf$facet, levels = c(trap.year, paste0(trap.year-5, '-', trap.year-1, ' Average')))

```


```{r Graph Creation, include = FALSE}  
# get Plot Max value for Y axis
plot_max_df <- LRW_catch %>%
  group_by(trapped_date) %>%
  summarize(Count = sum(Catch)) 
plot_max <- max(plot_max_df$Count)+2

# Calculate scale factor (for dual Y axes)
scaleFactor <- round(max(LRW_megadf$Catch, na.rm=TRUE)/max(LRW_megadf$MeanDailyFlow, na.rm=TRUE), 3)

# Plot
lrw_megaplot_sth <- ggplot(LRW_megadf, aes(x=trapped_date)) +
  # Data
  geom_bar(data = LRW_megadf, aes(x = trapped_date, y = Catch, fill = origin), color = 'black',
           stat='identity', position = 'stack', width = 1) +
  geom_line(data = LRW_megadf, 
            aes(x = trapped_date, y = MeanDailyFlow*scaleFactor, linetype= "Discharge"), 
            color = 'blue', size = 1) +
  # Y axis
  scale_y_continuous(name = 'Number of Steelhead', 
                     breaks = scales::breaks_pretty(7), 
                     limits = c(0, max(0, plot_max)),
                     expand = c(0, 0), sec.axis=sec_axis(~./scaleFactor, 
                     name = expression(paste("Discharge ("*ft^3*"/s)", sep='')), 
                     breaks = scales::breaks_pretty(7))) +
  # X Axis
  scale_x_date(name = '', labels = scales::label_date("%m/%d"), 
               breaks = scales::breaks_pretty(7), 
               expand = c(.001, .001)) +
  theme(
    axis.text.x = element_text(hjust = 1, angle = 45, size = 14),
    axis.ticks.length.x = unit(.15, "cm"),
    axis.title.y.left=element_text(size = 16),
    axis.text.y.left=element_text(size = 14),
    axis.title.y.right=element_text(color="blue", size = 16),
    axis.text.y.right=element_text(color="blue", size = 14),
    # panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.title = element_blank(), 
    legend.box.background = element_blank(), # element_rect(colour = "black")
    panel.spacing = unit(2, 'lines')
  ) + 
  guides(color = FALSE) +
  scale_fill_manual(values =c("Natural"='#FDE735FF', "Hatchery" = '#482677FF')) +
  facet_grid(rows=vars(facet))

```

```{r Data Processing: Weekly Steelhead Catch, eval = TRUE, include=FALSE}

# there is no steelhead brood
table_3 <- sumSTHweekly(data = lrw_omykiss, trap.year = trap.year)
```

\

### Disposition & Capture Summary

\

* The Lostine River weir started operating on March 1, 2023 and captured the first steelhead of the year on April 1, 2023.
* The weir has operated continuously except from 9:00 PM on May 2 to 7:00 AM on May 5, and 9:00 PM on May 17 to 8:00 AM on May 24, 2023 when it was inoperable due to high flows and debris.
* There is no supplementation program for Lostine River steelhead. However, this report shows all possible dispositions of fish captured at the Lostine River weir to remain consistent across different reporting species. 

\

```{r Table1_Hatchery_Dispositions, ft.align = 'center'}

flextable(hsth_df,
          cwidth = c(1.3,0.7,0.7,0.7,1.2,1.2)) %>%
  align(j=2:4, align = 'right', part = 'all') %>%
  hline(i=nrow(hsth_df)-1) %>%
  set_caption(caption = paste0('Table 1. Return year ',trap.year,' capture and disposition summary of hatchery steelhead (Numbers in parentheses exclude recaptures).'),
  style = "Table Caption")

```

<br>
<br>

```{r Table2_Natural_Dispositions, ft.align = 'center'}

flextable(nsth_df,
          cwidth = c(1.3,0.7,0.7,0.7,1.2,1.2)) %>%
  align(j=2:4, align = 'right', part = 'all') %>%
  hline(i=nrow(nsth_df)-1) %>%
  set_caption(caption = paste0('Table 2. Return year ',trap.year,' capture and disposition summary of natural steelhead (Numbers in parentheses exclude recaptures).'),
  style = "Table Caption")


```

\
\

```{r Table3_weekly_catch, ft.align = 'center'}
flextable(table_3,
          cwidth = c(1,1.5,1.5,1.2)) %>%
  align(j=2:4, align = 'center', part = 'all') %>%
  hline(i=nrow(table_3)-1) %>%
  set_caption(caption = paste0('Table 3. Return year ',trap.year,' weekly summary of captured steelhead and Rainbow Trout, excluding recaptures. *Asterisk indicates an incomplete week.'),
  style = "Table Caption")


```

\
\

### Current Arrival & Annual Run Timing

\

```{r figure1, eval=TRUE, fig.align='center', fig.cap= 'Figure 1. Return year 2023 (top panel) and five-year average (bottom panel) of mean daily discharge (cubic feet per second) and daily captures of hatchery- and natural-origin Steelhead at the Lostine River Weir. Discharge recorded at USGS station 1333000 located upstream of the town of Lostine.'}

lrw_megaplot_sth +
  labs(title = 'Daily capture of natural and hatchery steelhead at the Lostine River weir')

```

\
\

```{r figure2, eval=TRUE, fig.align='center', fig.cap= 'Figure 2. Daily capture of steelhead at the Lostine River weir. The red vertical line idicates current day of year.', fig.height=8 }

today = Sys.Date() %>% yday() %>% as.Date(origin = '1899-12-31')

stacked_histo <- lrw_omykiss %>%
  filter(species == 'Steelhead',
         trap_year %in% yr_range,
         recap == FALSE) %>%
  mutate(trap_day = yday(trapped_date)) %>%
  mutate(trap_day = as.Date(trap_day, origin = '1899-12-31')) %>%
  mutate(trap_year = as.factor(trap_year)) %>%
  ggplot(aes(x = trap_day)) +
  geom_histogram(binwidth = 1, color = 'black') +
  geom_vline(xintercept = today, color = 'red', size = 0.75) +
  facet_grid(trap_year ~ ., scales = 'free_y') +
  labs(x = 'Date of trapping',
       y = 'Unique fish count',
       title = 'Daily Capture of Steelhead at the Lostine River Weir')

stacked_histo

```

\
\

```{r table4_arrival, ft.align='center'}
# descriptive stats ------------------------------------------------
arrival_timing <- lrw_omykiss %>%
  filter(species == 'Steelhead',
         trap_year %in% yr_range,
         recap == FALSE) %>%
  mutate(trap_day = yday(trapped_date)) %>%
  group_by(trap, trap_year) %>%
  summarise(unique_fish = sum(count),
            first_fish = min(trap_day),
            perc_10 = quantile(trap_day, 0.1),
            median = quantile(trap_day, 0.5),
            perc_90 = quantile(trap_day, 0.9),
            last_fish = max(trap_day)) %>%
  mutate(across(c(first_fish, perc_10, median, perc_90, last_fish),
                as.Date, origin = '1900-01-01')) %>%
  mutate(across(c(first_fish, perc_10, median, perc_90, last_fish),
                format,'%b %d')) %>%
  ungroup()


arrival_timing %>%
  mutate(trap_year = as.character(trap_year)) %>%
  select(trap_year:last_fish) %>%
  flextable() %>%
  align(j = 2:6, align = 'center', part = 'all') %>%
  set_header_labels(trap_year = 'Year', unique_fish = 'Unique Fish', first_fish = 'First Capture', perc_10 = '10th Percentile', median = 'Median', perc_90 = '90th Percentile', last_fish = 'Final Capture') %>%
  set_caption(
  caption = paste0('Table 4. 10-year arrival timing of steelhead at the Lostine River Weir.'),
  style = "Table Caption")

```


\
\
\
<center>
**Distribution List**
</center>
\
\
\

:::: {style="display: grid; grid-template-columns: 1fr 1fr 1fr 1fr 1fr"}

::: {}

:::

::: {}
Beals, S (ODFW)  
Brady, A (BPA)  
Brandt, E (ODFW)  
Bratcher, K (ODFW)  
Brigante, E (ODFW)  
Bronson, P (CTUIR)  
Craft, N (ODFW)  
Deal, D (ODFW)  
Engle, R (FWS)  
Farnam, B (NOAA)  
Feldhaus, J (ODFW)  
Flesher, M (ODFW)   
Garza, Gabriel (ODFW)  
Gee, S (ODFW)  
Gibbs, A (ODFW)  
Greiner, M (ODFW)  
Hagenah, P (Wallowa CTY)  
Harbeck, J (NPT)  
Harrod, R (ODFW)  
Hesse, J (NPT)  
Humphreys, J (TU)  
Johnson, B (NPT)  

:::

::: {}

:::

::: {}

Johnson, D (NPT)  
Kozlowski, C (ODFW)  
Lovrak, J (CTUIR)  
Lance, M (ODFW)  
Lemanski, J (ODFW)  
Maxwell, A (TU)  
McLean, M (CTUIR)  
McOmie, E (BPA)  
Nisbitt, K (Wallowa CTY)  
Oatman, J (NPT)  
Robertson, M (FWS)  
Rumelhart, R (NPT)    
Treadway, E (ODFW)  
Smith, J (ODFW)  
Vatland, S (NPT)  
Vogel, J (NPT)  
Watry, C (NPT)  
Wiese, N (USFWS)  
Wolfe, W (Landowner)  
Yanke, J (ODFW)  
Yearout, J (NPT)  
Young, B (NPT)  
Zollman, R (NPT)

:::

::: {}

:::

::::

\
\
\
<center>
**Please direct questions regarding content of this report to:**  
\
**Brian Simmons**  
Grande Ronde Supplemenetation Monitoring and Evalutation  
Fisheries Biologist II  
541-432-2515  
brians@nezperce.org  
\
or  
\
**Shane Vatland**  
Grand Ronde Supplementation Monitoring and Evaluation  
Project Leader  
541-432-2508  
shanev@nezperce.org  
\
**Nez Perce Tribe**  
Joseph Field Office  
500 North Main Street  
P.O.Box 909  
Joseph, OR 97846
</center>
\
\
\
\
\
\


















